### 2018-09-16 sections/objects.tex
small fix from George

Overlaps between candidate objects are removed sequentially. In the $\Hbb$ search, firstly, electron candidates that lie 
within $\Delta R = 0.01$ of a muon candidate are removed to suppress contributions from muon bremsstrahlung. 
Overlaps between electron and jet candidates are resolved next, and finally, overlaps between remaining jet candidates 
and muon candidates are removed. Clusters from identified electrons are not excluded during jet reconstruction. 
In order to avoid double-counting of electrons as jets, the closest jet whose axis is within ${\Delta}R = 0.2$ of an electron 
is discarded. If the electron is within ${\Delta}R = 0.4$ of the axis of any jet after this initial removal, the jet is retained and  the electron is removed.
The overlap removal procedure between the remaining jet candidates and muon candidates is designed to remove those muons 
that are likely to have arisen in the decay chain of hadrons and to retain the overlapping jet instead. 
Jets and muons may also appear in close proximity when the jet results from high-$\pt$ muon bremsstrahlung, 
and in such cases the jet should be removed and the muon retained. Such jets are characterised by having very 
few matching inner-detector tracks. Selected muons that satisfy $\Delta R(\mu,{\textrm{jet}}) < 0.04+10~\gev/\pt^\mu$ are rejected
if the jet has at least three tracks originating from the primary vertex; otherwise the jet is removed and the muon is kept.
The overlap removal procedure in $\Htautau$ search is similar to that of the $\Hbb$ search, except that the
first step is the removal of $\tauhad$ candidates within $\Delta R=0.2$ of electrons or muons, and the last step is the
removal of jets whose axis lies within $\Delta R=0.2$ of the highest-$\pt$ (leading) or the two leading $\tauhad$ candidates (depending on the
analysis channel, see Section~\ref{sec:data_presel}). In addition, the muon--jet overlap removal is slightly different:
if a muon lies within $\Delta R = 0.2$ of the axis of a jet, the jet is removed if either it has fewer than three tracks originating from the 
primary vertex or it has a small $\pt$ compared to that of the muon (the $\pt$ of the jet is less than 50\% of the $\pt$ of the muon,
or the scalar sum of the $\pt$ of the tracks associated to the jet is less than 70\% of the $\pt$ of the muon).

>>>>

Overlaps between candidate objects are removed sequentially. In the $\Hbb$ search, firstly, electron candidates that lie 
within $\Delta R = 0.01$ of a muon candidate are removed to suppress contributions from muon bremsstrahlung. 
Overlaps between electron and jet candidates are resolved next, and finally, overlaps between remaining jet candidates 
and muon candidates are removed. Clusters from identified electrons are not excluded during jet reconstruction. 
In order to avoid double-counting of electrons as jets, the closest jet whose axis is within ${\Delta}R = 0.2$ of an electron 
is discarded. If the electron is within ${\Delta}R = 0.4$ of the axis of any jet after this initial removal, the jet is retained and  the electron is removed.
The overlap removal procedure between the remaining jet candidates and muon candidates is designed to remove those muons 
that are likely to have arisen in the decay chain of hadrons and to retain the overlapping jet instead. 
Jets and muons may also appear in close proximity when the jet results from high-$\pt$ muon bremsstrahlung, 
and in such cases the jet should be removed and the muon retained. Such jets are characterised by having very 
few matching inner-detector tracks. Selected muons that satisfy $\Delta R(\mu,{\textrm{jet}}) < 0.04+10~\gev/\pt^\mu$ are rejected
if the jet has at least three tracks originating from the primary vertex; otherwise the jet is removed and the muon is kept.
The overlap removal procedure in the $\Htautau$ search is similar to that of the $\Hbb$ search, except that the
first step is the removal of $\tauhad$ candidates within $\Delta R=0.2$ of electrons or muons, and the last step is the
removal of jets whose axis lies within $\Delta R=0.2$ of the highest-$\pt$ (leading) or the two leading $\tauhad$ candidates (depending on the
analysis channel, see Section~\ref{sec:data_presel}). In addition, the muon--jet overlap removal is slightly different:
if a muon lies within $\Delta R = 0.2$ of the axis of a jet, the jet is removed if either it has fewer than three tracks originating from the 
primary vertex or it has a small $\pt$ compared to that of the muon (the $\pt$ of the jet is less than 50\% of the $\pt$ of the muon,
or the scalar sum of the $\pt$ of the tracks associated to the jet is less than 70\% of the $\pt$ of the muon).
